Formalization of Network Flow Algorithms

### 2017-02-28 paper/root.tex
better node points for diagrams

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1000$, $2000$, $3000$, $4000$, $5000$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square}
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{fill=gray, mark=*}
      \addlegendimage{fill=gray, mark=o}
      \addlegendimage{fill=gray, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

@@

	\nextgroupplot[
    	title={Random Dense Graphs},
    	title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {1,4,...,16},
      xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
      yticklabels = {$1$,$4$,$8$,$12$,$16$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={Fully Dense Acyclic Networks (Waissi)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {0.01, 0.1, 0.2, 0.5, 1},
      xticklabels = {$1000$, $1100$, $1200$, $1300$, $1400$}, 
      yticklabels = {$0.01$, $0.1$,$0.2$,$0.5$,$1$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,23000,27000,30000},
      ytick = {0.1,1,5,10,25},
      xticklabels = {$16k$, $19k$, $23k$, $27k$, $30k$}, 
      yticklabels = {$0.1$, $1$,$5$,$10$,$25$}, 
      smooth,
      cycle list name = black white
	]

>>>>

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1k$, $2k$, $3k$, $4k$, $5k$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square}
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{fill=gray, mark=*}
      \addlegendimage{fill=gray, mark=o}
      \addlegendimage{fill=gray, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

@@

	\nextgroupplot[
    	title={Random Dense Graphs},
    	title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {2,4,6,10,16},
      xticklabels = {$1k$, $1.1k$, $1.2k$, $1.3k$, $1.4k$}, 
      yticklabels = {$2$,$4$,$6$,$10$,$16$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={Fully Dense Acyclic Networks (Waissi)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {0.01, 0.1, 0.2, 0.5, 1},
      xticklabels = {$1k$, $1.1k$, $1.2k$, $1.3k$, $1.4k$}, 
      yticklabels = {$0.01$, $0.1$,$0.2$,$0.5$,$1$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,23000,27000,30000},
      ytick = {0.1,3,6,12,24},
      xticklabels = {$16k$, $19k$, $23k$, $27k$, $30k$}, 
      yticklabels = {$0.1$, $3$,$6$,$12$,$24$}, 
      smooth,
      cycle list name = black white
	]
